ASTR480 Final Report:\\ \textit{Asteroids in TESS}

### 2024-10-15 FinalReport/FinalReportDraft.tex
done for last tues

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.7\textwidth]{../Test Code/Testing Figures/Diam-FreqPlot.pdf}
  \caption[Asteroid frequencies vs diameter (LCDB)]{The $U\geq 2-$ rotation frequencies in \unit{\per\day} and the inverse as a period in \unit{\hour} againts the diameter of the body in the October \nth{1}, 2023 LCDB \citet{Warner2009}.
  The axes are in log scale. 
  This is using the diameter of the asteroids from the LCDB $H$ to diameter conversion. 
  The spin barrier of \citet{Pravec2000} is shown in red dashed lines.
  }
  \label{Fig:FreqVsDiam}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width =\textwidth]{../OzData/SingleBodyLC1991 VT.pdf}
  \caption[Light curves Example]{The light curves of the asteroid 1991 VT throughout its entrie journey across sector 29, with the flux of the interpolated positions in blue circles and the flux from the COM in orange diamonds, and the \texttt{TESSELLATE} flux for any matched points in the black squares.
    The Flux axis is measured in counts, as calculated by \texttt{TESSreduce}, and the times are in modified Julian date (MJD).}
  \label{Fig:FullSingleLC}
\end{figure}
A comparison between the three light curves is interesting, as one might expect only the brightest parts of the lightcurve will be matched.
\autoref{Fig:FullSingleLC} shows these three light curves for a single body.
The COM flux seems much more stable than the interpolated positions flux on its own, and at a higher average flux count.
This should result in more accurate periodograms as there is less overall curve to the data.
The matched points are comparatively sparse for this object, which is not the case for all.
Many have no matches, and some have almost fully matched, this will be discussed more later.
Lightcurves with an average flux $<10$ counts are lost in the random noise floor, so a minimum mean flux limit needs to be applied to ensure quality and reliability of any periods calculated.

>>>>

\begin{figure}[t!]
  \centering
  \includegraphics[width=0.7\textwidth]{../Test Code/Testing Figures/Diam-FreqPlot.pdf}
  \caption[Asteroid frequencies vs diameter (LCDB)]{
  Rotaion rate of asteroids by their size, recreated from the  October \nth{1}, 2023 LCDB after \citet{Warner2009}.   
  }
  \label{Fig:FreqVsDiam}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width =\textwidth]{../OzData/SingleBodyLCUlyssesCorrectedAgain.pdf}
  \caption[Light curves Example]{The light curves of the asteroid (5254) Ulysses throughout its entire journey across sector 29, with the flux of the interpolated positions in blue circles and the flux from the COM in orange diamonds, and the \texttt{TESSELLATE} flux for any matched points in the black squares.
    The Flux axis is measured in counts, as calculated by \texttt{TESSreduce}, and the times are in modified Julian date (MJD).}
  \label{Fig:FullSingleLC}
\end{figure}
A comparison between the three light curves is interesting, as one might expect only the brightest parts of the lightcurve will be matched.
\autoref{Fig:FullSingleLC} shows these three light curves for a single body.
The COM flux seems much more stable than the interpolated positions flux on its own, and at a higher average flux count.
This should result in more accurate periodograms as there is less overall curve to the data.
The matched points are comparatively sparse for this object, which is not the case for all.
Many have no matches, and some have almost fully matched, this will be discussed more later.
Lightcurves with an average flux $<10$ counts are lost in the random noise floor, so a minimum mean flux limit needs to be applied to ensure quality and reliability of any periods calculated.
